Community Embeddings for Friend Suggestions

### 2020-10-11 conference_101719.tex
write intro on alg

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
proofreading, spelling and grammar.

>>>>

\section{Algorithm}

The proposed algorithm for generating friend suggestions using community embeddings is detailed and evaluated on time complexity. The initially quadratic runtime of generating friend suggestions for all users is then reduced by a factor of $K$ by utilizing a node's community membership. The two resulting algorithms are presented.

Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
proofreading, spelling and grammar.
